Start with the literature: assessthe empirical evidence for the relationship between ter-rorism and political attitudes

### 2024-02-13 outputs/paper/paper.qmd
update

---
title: "Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed"
author: "Jayden Jung, Finn Korol, Sofia Sellitto"
thanks: "Code and data are available at: https://github.com/jj-andj/mate-comp-hate ; Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-qg85-cb34"
date: "February 17, 2023"
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1in
    abstract: "Immigration and asylum-seeking are common topics of discussion in our globalized world, about which many Westerners hold opinions due to certain personal justifications. This paper replicates data analysis of the perceptions of non-immigrant German males towards refugees in municipalities where males overpopulate females. We apply secondary research regarding Canadian rates of immigration and gender imbalances in Alberta and raise concerns regarding the possibly generalizable nature of the findings in Germany. As this issue specifically affects minority groups experiencing prejudice, we place great emphasis on the weight of this discussion and call for future investigations of this field to inform policies and initiatives to address racism and hate crimes."
    number-sections: true
output: 
  bookdown::pdf_document2
toc: false
fig_caption: yes
nocite: '@*'
bibliography: references.bib
---

@@

In this paper we will replicate figure 2 and table2 of the orginal paper. Fortunately, the author has already compressed all the analysis into one coding file. We selected the corresponding part for each illustration. In terms of the analysis method, Pearson's correlation coefficient is used. According to the orignal paper, the manuscripts of the data they collected used various statistical method. For comparison purposes, each association is converted into a Pearson's correlation coefficient with the sampling variance. The author stressed that to "meaningfully compare and pool effect sizes, all correlations must also reflect the relation between terrorism and sociopolitical attitudes in the same direction."
# Results

>>>>

---
title: "Start with the literature: assessthe empirical evidence for the relationship between ter-rorism and political attitudes"
author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Jingcheng Yang"
thanks: "Code and data are available at: https://github.com/BerniceBao/Terrorism-Political-Attitude ; Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-qg85-cb34"
date: "February 13, 2024"
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1in
    abstract: "Immigration and asylum-seeking are common topics of discussion in our globalized world, about which many Westerners hold opinions due to certain personal justifications. This paper replicates data analysis of the perceptions of non-immigrant German males towards refugees in municipalities where males overpopulate females. We apply secondary research regarding Canadian rates of immigration and gender imbalances in Alberta and raise concerns regarding the possibly generalizable nature of the findings in Germany. As this issue specifically affects minority groups experiencing prejudice, we place great emphasis on the weight of this discussion and call for future investigations of this field to inform policies and initiatives to address racism and hate crimes."
    number-sections: true
output: 
  bookdown::pdf_document2
toc: false
fig_caption: yes
nocite: '@*'
bibliography: references.bib
---

@@

In this paper we will replicate figure 2 and table2 of the orginal paper. Fortunately, the author has already compressed all the analysis into one coding file. We selected the corresponding part for each illustration. In terms of the analysis method, Pearson's correlation coefficient is used. According to the orignal paper, the manuscripts of the data they collected used various statistical method. For comparison purposes, each association is converted into a Pearson's correlation coefficient with the sampling variance. The author stressed that to "meaningfully compare and pool effect sizes, all correlations must also reflect the relation between terrorism and sociopolitical attitudes in the same direction."

# Results
